Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-06 article.tex
Correct against many tests

To detect evolution, we determine the probability 
that all of the observed TMH mutations have arisen by chance,
with regards to being detected/presented by the immune system,
per MHC class and haplotype.
Because we use \richel{X} MHC-I and \richel{Y} MHC-II haplotypes
for a significance level of 5\%, by chance we expect \richel{X+Y/20}
times to find a haplotype that is suggested to have selection working 
upon it.

>>>>

To detect evolution, we determine the probability 
that all of the observed TMH mutations have arisen by chance,
with regards to being detected/presented by the immune system,
per MHC class and haplotype.

\paragraph{Correction against many tests}

Because we use \richel{X} MHC-I and \richel{Y} MHC-II haplotypes
for a significance level of 5\%, by chance we expect \richel{X+Y/20}
times to find a (MHC-I or MHC-II) haplotype 
that is suggested to have selection working 
upon it. Applying a binomial distribution ($p = 0.05$, $n = X+Y$, $\alpha = 0.05$),
we will claim we detected selection when we found \richel{Z} or
more examples of having a significant result.
